The GitHub Open Source Development Process \author{Kevin Peterson\\ Department of Information Technology\\ Clinical Informatics Support Systems\\ Mayo Clinic\\ 200 1st Street\\ Rochester, MN 55905\\ \small \texttt{peterson.kevin@mayo.edu} }

### 2013-04-29 paper/main.tex
Final set of typo fixes??? Maybe.

As \emph{watches} don't necessarily signal intent to contribute, a positive direction for an OSS project is to not only increase the number of \emph{watchers}, but also the number of \emph{forks}. As both signify a general general interest in the project, it is expected that there will be some correlation between the two.\\

@@

\noindent \textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A small core of developers contributing to a project seems to be a well entrenched pattern of OSS development~\cite{mockus2000case,mockus2002two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site Sourceforge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers~\cite{krishnamurthy2002cave}. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changed this?\\

@@

When a random repository has been selected, the \textsc{isOrgRepo} function will filter out all non \textit{Organization} owned repositories. Next, the \textsc{store} function accepts as an input the given repository. The purpose of this function is to persist the given repository to a database for further analysis. Results were stored in a MySQL relational database management system. The database schema to store the data is described in Figure~\ref{fig:er_diagram}.

\begin{figure}
\includegraphics[height=3in,width=3in]{images/er.png}
\caption{GitHub Date Entity Relationship diagram}
\label{fig:er_diagram}
\end{figure}

@@

\noindent \textbf{\textit{Issue Close Time:}}
The average time (in Days) taken to close a given issue in a repository. Non-\textsc{closed} issues were not counted.\\

The average \textit{issue close time} is calculated using the following method: Let $d(x)$ be a function that converts seconds to a Date, and let $s(x)$ be a function that converts a Date to seconds. Let $I$ equal the Set of \textit{Issues} in a given repository, with elements comprised of tuples $(\tau, \tau^\prime)$, where $\tau$ is \textit{Issue Open Date} and $\tau^\prime$ is \textit{Issue Close Date}. We calculate \textit{Issue Close Time} by:

@@

\subsection{Summary Statistics}
\label{sec:summary_statistics}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 1000 Repositories
\caption{GitHub Summary Statistics}
\label{table:summary_stats}
\end{center}
\end{table}

@@

\noindent \textbf{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
No significant correlation was found between the number of repository forks and issue resolution time. It is important to note, however, that issue resolution time is not necessarily related to software product quality in the context of GitHub. We can assert that for several reasons. \textit{First}, GitHub issues are not necessarily product defects. Issues may be feature requests, comments, or general support questions. \textit{Second}, GitHub projects may have primary issue tracking services elsewhere, while using the GitHub issues as secondary services or not at all. \textit{Third}, Cultural shifts in how testing is approached may have significant impact on quality. Pham \textit{et al.} explore an emerging ``testing culture'' in GitHub, which suggests that GitHub may be facilitating testing by making it more \emph{triable} by lowering entry barriers, and makng the process as a whole more \emph{observable}. This aspect is something which could have sizable impacts on software quality but wouldn't necessarily be reflected in this metric~\cite{phamcreating}.

\begin{figure}
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}
\caption{Repository issue close time and number of forks}
\label{fig:issue_close_time_forks_scatterplot}
\end{figure}

@@

Where $U$ is the Set of \textit{Committers} to a given \textit{Repository}, $\mathscr{C}$ is the set of all \textit{Commits} to a \textit{Repository}, and $C_u$ denotes sets of \textit{Commits} by an individual \textit{Committers} to a \textit{Repository}, or:
 \[ \{ C_u \}_{u \in U} \]

>>>>

As \emph{watches} don't necessarily signal intent to contribute, a positive direction for an OSS project is to not only increase the number of \emph{watchers}, but also the number of \emph{forks}. As both signify a general interest in the project, it is expected that there will be some correlation between the two.\\

@@

\noindent \textbf{Research Question 1: Are GitHub projects primarily focused around a small set of core Committers?}\\
A small core of developers contributing to a project seems to be a well entrenched pattern of OSS development~\cite{mockus2000case,mockus2002two,krishnamurthy2002cave}. At the extreme of this, a study of projects on the software hosting site SourceForge\footnote{http://sourceforge.net} found that a large percentage of OSS development is done by lone developers~\cite{krishnamurthy2002cave}. Is a small core of developers intrinsic to OSS development, or have the social aspects of GitHub and the distributed nature of Git changed this?\\

@@

To select a repository, a random word is selected from an arbitrary list via the \textsc{random}($word\_list$) function. Using the GitHub search API, a list of repositories containing that word in the description is retrieved using the \textsc{github\_search}($word$) function, from which a one is randomly select using \textsc{random}($repos$). When a random repository has been selected, the \textsc{isOrgRepo} function will filter out all non \textit{Organization} owned repositories. Next, the \textsc{store} function accepts as an input the given repository. The purpose of this function is to persist the given repository to a database for further analysis. Results were stored in a MySQL relational database management system. The database schema to store the data is described in Figure~\ref{fig:er_diagram}.

\begin{figure}
\includegraphics[height=3in,width=3in]{images/er.png}
\caption{GitHub data entity relationship diagram}
\label{fig:er_diagram}
\end{figure}

@@

\noindent \textbf{\textit{Issue Close Time:}}
The average time (in days) taken to close a given issue in a repository. Non-\textsc{closed} issues were not counted.

The average \textit{Issue Close Time} is calculated using the following method: Let $d(x)$ be a function that converts seconds to a Date, and let $s(x)$ be a function that converts a Date to seconds. Let $I$ equal the Set of \textit{Issues} in a given repository, with elements comprised of tuples $(\tau, \tau^\prime)$, where $\tau$ is \textit{Issue Open Date} and $\tau^\prime$ is \textit{Issue Close Date}. We calculate \textit{Issue Close Time} by:

@@

\subsection{Summary Statistics}
\label{sec:summary_statistics}
\begin{table}[!ht]
\begin{center}
\begin{tabular}{rrrrrrr}
\hline
Variable & Mean & Min & Max & Std. Dev. \\
\hline
\input{summary_statistics}
\hline
\end{tabular}
N = 1000 Repositories
\caption{GitHub summary statistics}
\label{table:summary_stats}
\end{center}
\end{table}

@@

\noindent \textbf{Hypothesis 2: As the number Repository Forks increase, the Issue Resolution Time will decrease.}\\
No significant correlation was found between the number of repository forks and issue resolution time, as shown by the data represented in Figure~\ref{fig:issue_close_time_forks_scatterplot}. It is important to note, however, that issue resolution time is not necessarily related to software product quality in the context of GitHub. We can assert that for several reasons. \textit{First}, GitHub issues are not necessarily product defects. Issues may be feature requests, comments, or general support questions. \textit{Second}, GitHub projects may have primary issue tracking services elsewhere, while using the GitHub issues as secondary services or not at all. \textit{Third}, cultural shifts in how testing is approached in GitHub may have significant impacts on software quality. Pham \textit{et al.} explore an emerging ``testing culture'' in GitHub, which suggests that GitHub may be facilitating testing by making it more \emph{triable} by lowering entry barriers, and making the process as a whole more \emph{observable}. This aspect is something which could have sizable impacts on software quality but wouldn't necessarily be reflected in this metric~\cite{phamcreating}.

\begin{figure}
\includegraphics[height=3in,width=3in]{images/issue_close_time_forks_scatterplot.png}
\caption{Repository issue close time (in days) and number of forks}
\label{fig:issue_close_time_forks_scatterplot}
\end{figure}

@@

Where $U$ is the set of \textit{Committers} to a given \textit{Repository}, $\mathscr{C}$ is the set of all \textit{Commits} to a \textit{Repository}, and $C_u$ denotes sets of \textit{Commits} by an individual \textit{Committers} to a \textit{Repository}, or:
 \[ \{ C_u \}_{u \in U} \]
